Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-26 paper/sec/formalization_neg_dep.tex
Explain incompleteness of Joag-devs proof regarding neg. association of permutation distributions.

We relied on the proof by Dubashi using the FKG inequality~\cite[Th. 10]{dubhashi1996}; there is a prior proof by Joag-Dev and Proschan~\cite[Th. 2.11]{joagdev1983}, which seemed to be incorrect.

>>>>

We relied on the proof by Dubashi et al.\ using the FKG inequality~\cite[Th. 10]{dubhashi1996}; there is a prior proof by Joag-Dev and Proschan~\cite[Th. 2.11]{joagdev1983}, which is incomplete\footnote{The step which we could not directly formalize is the assertion (Sentence~14) in the proof of Theorem~2.11 (\cite{joagdev1983}) that the conditional expectation of the random variable $f(X)$ is smaller iff the smallest element of the permutation is contained in $\mathrm{dep}(f)$. That statement is non-trivial and requires a proof using a theorem such as the FKG-inequality. We think Dubashi et al.\ developed their proof to complete it.}.
